Simulation Tools for Small Area Estimation: Introducing the \proglang{R}-package \proglang{saeSim}

### 2015-01-26 replies_to_referee/Replies_to_referee.tex

%\begin{abstract}
%This is the abstract
%\end{abstract}

%\textbf{Keywords:} These are the keywords.

%\doublespacing

We are very grateful to the Editor and the two reviewers for their constructive comments. These have been very helpful in preparing the revised version of this paper. We have done our best to incorporate them in the revision. The following notes explain how we addressed each comment.

@@

\vspace{0.5cm}

\noindent There are only minor issues that need to be addressed.

\begin{itemize}
\item
	Page 2: The authors cite Kolb (2013) for synthetic data generation. They should also mention what is available in R, for instance the approach by Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) that is implemented in package simPop.

	Reply: We now reference Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) together with Kolb (2013). The R-package simPop is now mentioned in the paragraph where we also cite simFrame, also on page 2.

@@

\item
	Page 2: The authors mention NUTS levels without explaining what they are. Please add a short explanation, including what the abbreviation NUTS stands for.

	Reply: We deleted the reference to the NUTS levels. After the revision the paragraph doesn't lose relevant information to follow the common theme. The revised version is now as follows:\\\\
	\textit{
	Survey statistics are used, for example, in order to deliver specific indicators as a basis for
economic and political decision processes. Especially regional or group-specific comparisons
are of interest (cf. Schmid and M\"unnich 2014). Surveys which shall provide sufficient data
for these regional indicators, however, are generally designed for larger areas. Hence, sample
information on more detailed levels, e.g. municipalities, is hardly available so that classical
estimation methods (direct estimators) may lead to high variances of the estimates (cf. Ghosh
and Rao 1994). In this case, small area estimation methods may reveal highly improved results
for the target estimates. Small area estimation has become more and more attractive over
the last decade:
	}

@@

\item
	Page 5, last paragraph: I'm not sure which line in the simple example for the pipe operator is more readable. The line "sum(1:10)" translates into "sum of 1 to 10". The line "1:10 \%$>$\% sum" tanslates into "generate 1 to 10, then take the sum". I'm sure that the authors can find a simple example that is better suited to illustrate their point.

	Reply: We acknowledge that we have to be more specific here. We changed the example to:
	\verb'colMeans(matrix(rnorm(10), ncol = 2))' which translates to \\\verb'rnorm(10) %>% matrix(ncol = 2) %>% colMeans'.

@@

\item
	Page 6 and 7, code examples: The authors load package saeSim in each of the two code examples. Yet there is another code chunk before those examples which use functionality from the package. If readers try to execute all code in the order it appears in the paper, they will get error messages. I suggest to load the package in the beginning of Section 4 (in a separate chunk), and to remove this line from the two examples to focus on the relevant code.

	Reply: We load now saeSim (and magrittr) in the beginning of section 4. We checked the code again, so that all expressions are valid when executed in the order in which they appear in the article. We also made the seed available to the reader. Furthermore the package sae produced naming conflicts as it loads a lot of dependencies. We do not load the package but reference to it with the '::' operator.

@@

\item
	Page 8, last line: The authors write "... we store these data tables...". Are those data frames or data tables? In R, this can be confusing due to the data.table package.

	Reply: To avoid any confusion we changed it into 'data frame'. The paragraph is quoted as a reply to you next remark.

\item
	Page 9: The authors state that they store some information as attributes to the main data frame. Attributes can be a dangerous thing in R as there are some functions for manipulating data that may remove any attributes. Please give a discussion on this issue and provide more motivation for using attributes.

Reply: We agree that relying on attributes may be dangerous in R. The problem is that in some situation we have to process a single data frame plus some meta data. An alternative is to make that meta data available by taking advantage of R's lexical scoping rules. However, this may be a dangerous path as the functions, which need the meta data, are no longer self contained. They depend on the specific state of the objects instead of their arguments. We want to avoid this situation. Another possibility is to make meta data available only to the functions in which they are needed by using closures. This ensures that the functions are self contained but adds unnecessary complexity because advanced functional programming techniques are not "mainstream" for R users. We also could design an own \textit{data class} which is more formal to ensure type consistency (for example using a S4-class). However, we tried to design saeSim such that it can be used with as many existing tools as possible. We think this is possible by sticking to the "data.frame in, data.frame out" philosophy. Thus, we decided to support functions which preserve attributes. All present functions in the package will preserve attributes of the main data frame. We have added the following paragraph in the paper (Section 4.2):\\\\
	\textit{
	Before we begin to construct the simulation setup, we store these data frames as attributes to the population data. This allows us to process on the same time a single data frame and some meta data. It is important to notice that some functions for manipulating data frames in R don't preserve their attributes. The prospective user of the saeSim has to keep this in mind when implementing user defined functions. However, all functions in saeSim are able to preserve their attributes. Other options can be applied within the possibilities of the R language. For instance, one could use closures to make the meta data only available for specific functions. This approach needs advanced functional programming skills and may add an additional level of complexity to the package user. However, from our perspective, adding attributes to the data is be a very flexible form of processing data on different aggregation levels and is used in this package.
	}
\item
	Page 13: To the best of my knowledge, the preferred format for CRAN links is http://CRAN.R-project.org/package=saeSim (also note the capitalization of CRAN and R).

    Reply: This has been corrected.
\item
	Page 13: For non-representative outliers, the authors give the explanation "outliers are part of the sample but not the population". This may be confusing to some readers. I suggest that they add "e.g., incorrectly recorded values".

Reply: This has been added.

@@

\end{itemize}

\vspace{0.5cm}

\noindent Comments regarding language are given in the following. There may be more mistakes, hence I recommend that the authors ask a colleague to proofread the manuscript (preferably an English native speaker).

\noindent Reply: We strongly apology for the mistakes in the article. We did a careful double check of the paper. In addition, we followed your suggestion to check the manuscript by an English native speaker.

\begin{itemize}
\item
	Page 1, abstract and first paragraph: "has been substantially grown" to "has grown" -- done
\item
	Page 3, line -8: "is build on a sampling model" to "is built on a sampling model" -- done
\item
	Page 4, line -2: "different point of views" to "different points of view" -- done
\item
	Page 6, lines 1-2: "In saeSim, we rely on this operator, although all functions can be used without, we strongly recommend to use it." to "In saeSim, we rely on this operator. Although all functions can be used without it, we strongly recommend its usage." -- done
\item
	Page 6, second paragraph: "... which has a data.frame as input as well as return value." The correct "... which has a data.frame as input as well as as return value." is cumbersome since as appears twice in a row, so I suggest to change this to "... which has a data.frame both as input and as return value."  -- done

@@

\item
	Page 10, first paragraph: "This focus on the definition of each component and on meeting the convention of the defined interface is the intended approach." I'm confused by this sentence, please rephrase.

	Reply: We acknowledge that the sentence may create some confusion to the prospective reader. Therefore, we have deleted to sentence to make the paragraph more clear. In the revised version of the paper we say the following:\\\\
	\textit{
		In the next step, we define components which add the estimates of interest to the data. Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model. Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independent of each other. This automatically organises the simulation and each component is arranged using the simulation framework. Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
		}
\item
	Page 13, second paragraph: "version-control" to "version control". -- done
\item
	Page 13, second paragraph: "it's purpose" to "its purpose". -- done
\end{itemize}

@@

\pagebreak
\section*{Replies to reviewer C}

The package appears to be useful for most statisticians working with small area methods. It is a good idea to build the framework using the idea of process of data manipulation. This makes the package easy to use. The manuscript is interesting and useful, and I find it acceptable for
publishing after minor revision.

\begin{itemize}
\item
	The authors should mention - probably in Section 4 - that in order to repeat a simulation with identical results, the seed used in the original simulation has to be known.

	Reply: We agree with this comment. We have added this information right before we start illustrating the model-based simulation. We have also added the seed in the code. In the first version, the seed was set in a hidden chunk. In Section 4.1 in the revised version of the paper we say the following:\\\\
	\textit{In this case the \textit{base-component} is a data frame with an id variable named idD and constructed with the function base\_id. Any random number generator in R can be used. However, we have normally distributed variates, for which some predefined functions are available in the package. For the reproducibility of the following results we also set the seed to 1. The seed is not part of a simulation setup in saeSim but needs to be defined by the researcher.}

@@

\end{itemize}

\vspace{0.5cm}

\noindent There are some grammatical errors:

\noindent Reply: We strongly apology for the grammatical errors in the article. We did a careful double check of the paper. In addition, the manuscript was checked by an English native speaker.

\begin{itemize}
\item[(1)]abstract: remove 'been' from "...has been substantially grown" -- done
\item[(2)]Introduction: remove 'been' from "...has been substantially..."-- done
\item[(3)]Introduction (last two lines on page 1): rephrase "...reproducible research aims that the full output of the academic research,..." using "...aims at the availability of the full... " -- done
\item[(4)]Replace 'neighboured' by 'neighbouring' -- done
\item[(5)]At the end of page 1, remove '-' in "source-code" -- done
\item[(6)]In the beginning of section 2 (second line), replace 'less' by 'few' in "...for domains where less or no sampled..." -- done
\item[(7)]Below equation (1), replace 'build' by 'built' in "...introduced by Fay and Herriot (1979) is build..." -- done
\end{itemize}

### 2015-01-26 saeSim.Rnw
saeSim corrections

%% an abstract and keywords
\Abstract{
The demand for reliable regional estimates from sample surveys has substantially grown over the last decades. Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators. Model- and design-based simulations are used to gain insights into the quality of the introduced methods. In this article we present a framework which may help to guarantee the reproducibility of simulation studies in articles and during research. The introduced \proglang{R}-package \proglang{saeSim} is adjusted to provide a simulation environment for the special case of small area estimation. The package may allow the prospective researcher during the research process to produce simulation studies with a minimal effort of coding.   
}

@@

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\red}[1]{\color{red} #1 \color{black} }

\begin{document}
%
%% include your article here, just as usual
%
% R CMD Sweave %.Rnw
% Loading (and installing) necessary packages.
<<echo=FALSE>>=
# loadAndInstallPackage <- function(packageName) {
#   if(!eval(substitute(suppressPackageStartupMessages(require(packageName))))) {
#     install.packages(packageName)
#     eval(substitute(suppressPackageStartupMessages(library(packageName))))
#   } 
# }
# loadAndInstallPackage("saeSim")
# # Keep order in which packages are loaded, there are naming conflicts between dependencies (MASS and dplyr) which are loaded and attached by the package sae:
# loadAndInstallPackage("sae")
# loadAndInstallPackage("dplyr")
# loadAndInstallPackage("reshape2")
# loadAndInstallPackage("ggplot2")
@
%
\section{Introduction}
The demand for reliable small area statistics from sample surveys has substantially grown over the last decades due to their use in public and private sectors. In this paper we present a framework for simulation studies inside the field of small area estimation. This tool might be useful for the prospective researcher or data analyst to provide reproducible research.

@@

Next to the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational environment like data and source code. However, real data is often very sensitive and governed by strict confidentiality rules. Synthetic data generation mechanisms as discussed in \cite{alfons2011} or \cite{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results. \cite{Bur14} interpreted this as an open research philosophy. Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework. 
%This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios. 
In general, simulation studies in statistics can be divided into two concepts:
%
\begin{itemize}
\item Design-based: The simulation study is based on true or synthetic data of a fixed population. Then, samples are selected repeatedly from the underlying finite population and different estimation methods are applied in each replication. The obtained estimates are compared to the true values of the population, for instance, in terms of relative bias (RB) or relative root mean squared error (RRMSE).
\item Model-based: The simulation study uses data drawn from certain distributions. In each iteration, the population is generated from a model and a sample is selected according to a specific sampling scheme. The sample is used to estimate the quantity of interest and quality measures (like RB and RRMSE) are derived.  
\end{itemize}
Further discussion regarding model- and design-based simulations is available in \cite{Mue03}, \cite{Sal10} or \cite{Alf10}.

@@

Survey statistics are used, for example, in order to deliver specific indicators as a basis for economic and political decision processes. Especially regional or group-specific comparisons are of interest \citep[cf.][]{Sch13}. Surveys which shall provide sufficient data for these regional indicators, however, are generally designed for larger areas. Hence, sample information on more detailed levels, e.g. municipalities, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}. In this case, small area estimation methods may reveal highly improved results for the target estimates. Small area estimation has become more and more attractive over the last decade:

@@

However, simulation studies in the context of small area estimation are often presented very briefly. Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis. To the best of our knowledge, there is not any \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.

The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible. To be more precise, the package has three main objectives: First, provide tools for data generation. Second, unify the process of simulation studies. Third, make the source code of simulation studies available, such that it supports the conducted research in a transparent manner.

The paper is organised as follows. In Section \ref{sec:SAE} we give a short introduction to small area estimation focusing mainly on unit-level \citep{battese88} and area-level models \citep{fay79}. Section \ref{sec:framework} introduces a framework for simulation studies and how it is supported by the  \proglang{R}-package \proglang{saeSim}. To illustrate some of the features of the package we present a model- and design-based simulation study in Section \ref{sec:caseStudy}. We conclude the paper in Section \ref{sec:outlook} by summarising the main findings and by providing some avenues for further research.

@@

The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available. Groups may be areas or other entities, for example defined by socio-economic characteristics. The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}. As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighbouring or \textit{similar} domains. This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with small sample sizes.

@@

\section{A simulation framework}
\label{sec:framework}
%
%% flow-diagram
\begin{wrapfigure}{R}{0.5\textwidth}
\begin{center}
\includegraphics[width=0.5\textwidth]{flowdiagram}
\end{center}
\caption{\label{fig:flowdiagram}Process of simulation. Left column are the steps in a simulation. Right column are the corresponding function names to represent those steps in \proglang{R}.} 
\end{wrapfigure}
%
In this section we will present the simulation framework implemented in \proglang{saeSim}. The framework relies strongly on the idea to describe a simulation as a process of data manipulation. Independent of simulation studies, \cite{wickham14a} and \cite{wickham14b} strongly promote this idea by providing tools for cleaning and transforming data. In those frameworks every defined function takes a \proglang{data.frame} as input and returns it modified. This leads to a natural connection between all defined functions as the result of one function can be directly passed to the next as an argument. The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only emphasises the process of data manipulation. To avoid nested function calls the operator can be used to improve the readability as expressions can be read from left to right (cf. Section \ref{sec:caseStudy}).

In \proglang{saeSim} we extend this approach to simulation studies in the field of small area estimation. The main focus lies on the description of a simulation as a process of data manipulation. Each step in this process can be defined as a self contained component (function) and thus can be easily replaced, extended and most importantly reused. Before we go into details of the functionality of the package we discuss the process behind simulation studies and how \proglang{saeSim} maps this process into \proglang{R}.

Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level. Figure \ref{fig:flowdiagram} illustrates these levels. The left column describes the steps of data manipulation, the right column presents the function names to define the corresponding steps. The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model. We see two different points of view to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population. Secondly, \textit{model-based} simulations, which have changing random populations drawn from a model.

The scope of this article is not to promote any of those viewpoints, we just want to incorporate the different simulation concepts in a common framework. The \textit{base} (first component in Figure \ref{fig:flowdiagram}) of a simulation study is a data table, the question is, if this data is \textit{fixed} or \textit{random} over simulations. Or from a more technical point of view, is the data generation (the second step in Figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted. Depending on the choice of a fixed or random population it is necessary to recompute the population domain-statistics like domain means and variances, or other statistics of interest (third component in Figure \ref{fig:flowdiagram}).

The \textbf{sample-level} is necessary when domain predictions are conducted for unit-level models. Independently of how the population is treated, fixed or random, this phase consists of two steps: Firstly, draw a sample according to a specific sampling scheme. Secondly, conduct computations on the samples (fourth and fifth component in Figure \ref{fig:flowdiagram}). Given a sample, small area methods are applied. Of interest are, for instance, estimated model parameters, domain predictions or measures of uncertainty (MSE) for the estimates.

As the sample-level is necessary when unit-level models are applied, the \textbf{aggregate-level} is conducted when area-level models are applied (the seventh and last component in Figure \ref{fig:flowdiagram}). Area-level models in small area estimation typically only use information available for domains (in contrast to units). Thus, the question for simulation studies for area-level methods is, if the data is generated on unit-level and is used after the aggregation (sixth component in Figure \ref{fig:flowdiagram}) or if the data is generated directly on area-level, i.e. drawn from an area-level model. Depending on whether unit-level data and sampling are part of the simulation process, the aggregate-level follows the generation of the population or is based on the aggregated sample. %Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.

@@

From this considerations, \proglang{saeSim} maps the different steps into \proglang{R}. Two layers with separate responsibilities need to be discussed. The first is \textit{how} different simulation components can be combined, and the second is \textit{when} they are applied. Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component. To be precise, we use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value. The return value of one component is the input of the next. This definition of interfaces is used for all existing tools in \proglang{saeSim}. The second column in Figure \ref{fig:flowdiagram} shows how the different steps in a simulation can be accessed. It is important to note that the functions in Figure \ref{fig:flowdiagram} control the process, the second layer, i.e. \textit{when} components are applied. Each of these functions take a simulation setup object to be modified and a function with the discussed interface as arguments. Hence, the pipe operator (\proglang{\%>\%}) can be used to combine separate components to a simulation setup.

\section{Case studies}
\label{sec:caseStudy}
We present two applications of \proglang{saeSim}, one model-based simulation in Section \ref{sec:csModel} and a design-based simulation in Section \ref{sec:csDesign}. Before, we introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation. The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}. As a simple example see the following lines which are equivalent with respect to their functionality:

@@

Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we notice that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme. \proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples. Separating the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process. The composition of a simulation in that manner will focus on the definition of components and hide control structures. Any function can be passed to \proglang{sim\_sample} which has a \proglang{data.frame} both as input and as return value. The only responsibility of that function is to draw a sample, which makes it easy to find, understand and reuse when published. The operator \proglang{\%>\%} is used to add new components to the setup.

@@

Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows (the head) of the resulting data table are printed. This enables interactivity with the object itself, however, it hides that the setup object is a collection of functions to be called. In this model the error component $e_i$ has different variances which is not covered by a predefined function. Thus, as a \textit{generator component}, we define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:

@@

To add the area-level predictions from a Fay-Herriot model we need to define another component. The function takes a \proglang{data.frame} as input and returns the modified version. For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}. Hence, we define a function named \proglang{comp\_FH} and add it to the process:

@@

An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios. At this time we do not provide further tools to process the resulting data as there are many tools readily available in \proglang{R}. In the design-based scenario we show how to process the result data into graphs with only a few lines of code.

@@

In the design-based simulation we illustrate the use of \proglang{saeSim} under a fixed population. For this purpose we use a synthetic population generated from Austrian EU-SILC (European Union Statistics on Income and Living Conditions) data. The data consists of 25 thousand households. It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is also used as an example data set. To keep this study as simple as possible, we further restrict the data on the main income holder and only use some of the provided auxiliary information.

@@

Before we come to the estimation, the first step is to add a sampling scheme. As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data. Then the sampling component is added, in which we define to draw 10 per cent sample of the observations from each domain with simple random sampling.

>>>>

%% an abstract and keywords
\Abstract{
The demand for reliable regional estimates from sample surveys has substantially grown over the last decades. Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators. Model- and design-based simulations are used to gain insights into the quality of \red{the methods utilized}. In this article we present a framework \red{which may help to support }the reproducibility of simulation studies in articles and during research. \red{The \proglang{R}-package \proglang{saeSim} is adjusted} to provide a simulation environment for the special case of small area estimation. The package may allow the prospective researcher during the research process to produce simulation studies \red{with minimal coding effort.}   
}

@@

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\red}[1]{\textcolor{red}{#1}}

\begin{document}
%
%% include your article here, just as usual
%
% R CMD Sweave %.Rnw
% Loading (and installing) necessary packages.
<<echo=FALSE>>=
# loadAndInstallPackage <- function(packageName) {
#   if(!eval(substitute(suppressPackageStartupMessages(require(packageName))))) {
#     install.packages(packageName)
#     eval(substitute(suppressPackageStartupMessages(library(packageName))))
#   } 
# }
# loadAndInstallPackage("saeSim")
# # Keep order in which packages are loaded, there are naming conflicts between dependencies (MASS and dplyr) which are loaded and attached by the package sae:
# loadAndInstallPackage("sae")
# loadAndInstallPackage("dplyr")
# loadAndInstallPackage("reshape2")
# loadAndInstallPackage("ggplot2")
@
%
\section{Introduction}
The demand for reliable small area statistics from sample surveys has substantially grown over the last decades due to their use in public and private sectors. In this paper we present a framework for simulation studies \red{within} the field of small area estimation. This tool might be useful for the prospective researcher or data analyst to provide reproducible research.

@@

\red{Besides }the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational \red{environment, like} data and source code. However, real data is often very sensitive and governed by strict confidentiality rules. Synthetic data generation mechanisms as discussed in \cite{alfons2011} or \cite{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results. \cite{Bur14} interpreted this as an open research philosophy. Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework. 
%This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios. 
In general, simulation studies in statistics can be divided into two concepts:
%
\begin{itemize}
\item Design-based: The simulation study is based on true or synthetic data of a fixed population. Then, samples are selected repeatedly from the underlying finite population and different estimation methods are applied in each replication. The estimates so obtained are compared to the true values of the population, for instance, in terms of relative bias (RB) or relative root mean squared error (RRMSE).
\item Model-based: The simulation study uses data drawn from certain distributions. In each iteration, the population is generated from a model and a sample is selected according to a specific sampling scheme. The sample is used to estimate the quantity of interest \red{for which} quality measures (like RB and RRMSE) are derived.  
\end{itemize}
Further discussion regarding model- and design-based simulations is available in \cite{Mue03}, \cite{Sal10} or \cite{Alf10}.

@@

Survey statistics are used, for example, in order to deliver specific indicators as a basis for economic and political decision processes. \red{Of special interest here are regional or group specific comparisons \citep[cf.][]{Sch13}. Surveys which are utilized to report these regional indicators, however, are generally designed for larger areas.} \red{Hence sample} information on more detailed levels, e.g. municipalities, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}. \red{In this case small} area estimation methods may reveal highly improved results for the target estimates. Small area estimation has become more and more attractive over the last decade:

@@

However, simulation studies in the context of small area estimation are often presented very briefly. \red{Thus there is }a need to have \red{a suitable framework} to guarantee the reproducibility of analysis. To the best of our knowledge, \red{there is no} \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.

The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible. To be more precise, \red{the suggested package} has three main objectives: First, \red{to provide} tools for data generation. Second, \red{to unify} the process of simulation studies. Third, \red{to make} the source code of simulation studies available, such that it supports the conducted research in a transparent manner.

\red{This paper} is organised as follows. In Section \ref{sec:SAE} we give a short introduction to small area estimation focusing mainly on unit-level \citep{battese88} and area-level models \citep{fay79}. Section \ref{sec:framework} introduces a framework for simulation studies and how it is supported by the  \proglang{R}-package \proglang{saeSim}. To illustrate some of the features of the package we present a model- and design-based simulation study in Section \ref{sec:caseStudy}. We conclude the paper in Section \ref{sec:outlook} by summarising the main findings and by providing some avenues for further research.

@@

\red{The aim} of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available. Groups may be areas or other entities \red{defined, for example, by} socio-economic characteristics. The demand for such estimators \red{is increasing} as they are used for fund allocation, educational and health programs \citep{pfeffermann13}. As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighbouring or \textit{similar} domains. This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with small sample sizes.

@@

\section{A simulation framework}
\label{sec:framework}
%
%% flow-diagram
\begin{wrapfigure}{R}{0.5\textwidth}
\begin{center}
\includegraphics[width=0.5\textwidth]{flowdiagram}
\end{center}
\caption{\label{fig:flowdiagram}Process of simulation. Left column are the steps in a simulation. Right column are the corresponding function names to represent those steps in \proglang{R}.} 
\end{wrapfigure}
%
In this section we will present the simulation framework implemented in \proglang{saeSim}. The framework relies strongly on the idea to describe a simulation as a process of data manipulation. Independent of simulation studies, \cite{wickham14a} and \cite{wickham14b} strongly promote this idea by providing tools for cleaning and transforming data. In those frameworks every defined function takes a \proglang{data.frame} as input and returns it modified. This leads to a natural connection between all defined functions \red{since} the result of one function can be directly passed to the next as an argument. The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only \red{emphasizes} the process of data manipulation. To avoid nested function calls the operator can be used to improve the readability as expressions can be read from left to right (cf. Section \ref{sec:caseStudy}).

In \proglang{saeSim} we extend this approach to simulation studies in the field of small area estimation. \red{The main focus lies in} the description of a simulation as a process of data manipulation. Each step in this process can be defined as a self contained component (function) and thus can be easily replaced, extended and most importantly reused. Before we \red{go into the details} of the functionality of the package we discuss the process behind simulation studies and how \proglang{saeSim} maps this process into \proglang{R}.

Simulation studies in small area estimation address three \red{different levels; these are the population}, the sample and data on aggregated level. Figure \ref{fig:flowdiagram} illustrates these levels. The left column describes the steps of data manipulation, the right column presents the function names to define the corresponding steps. The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model. We see two different points of view to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population. Secondly, \textit{model-based} simulations, which have changing random populations drawn from a model.

\red{The scope of this article is not to opt for viewpoints. The aim is to incorporate the different simulation concepts in a common framework.} The \textit{base} (first component in Figure \ref{fig:flowdiagram}) of a simulation study \red{is a data table; here the question is whether this data is \textit{fixed} or \textit{random} over simulations}. Or from a more technical point of view, is the data generation (the second step in Figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted. Depending on the choice of a fixed or random population it is necessary to \red{re-compute} the population domain-statistics like domain means and variances, or other statistics of interest (third component in Figure \ref{fig:flowdiagram}).

The \textbf{sample-level} is necessary when domain predictions are conducted for unit-level models. Independently of how the population is treated \red{- whether as fixed or random - }this phase consists of two steps: \red{Firstly, drawing} a sample according to a specific sampling scheme. {Secondly, conducting} computations on the samples (fourth and fifth component in Figure \ref{fig:flowdiagram}). Given a sample, small area methods are applied. Of interest are, for instance, estimated model parameters, domain predictions or measures of uncertainty (MSE) for the estimates.

\red{Since the sample-level} is necessary when unit-level models are applied, the \textbf{aggregate-level} is conducted when area-level models are applied (the seventh and last component in Figure \ref{fig:flowdiagram}). Area-level models in small area estimation typically only use information available for domains (in contrast to units). \red{Thus, the question for simulation studies for area-level methods is, whether the data is generated on unit-level and is used after the aggregation (sixth component in Figure \ref{fig:flowdiagram}) or the data is generated directly on area-level, i.e. drawn from an area-level model. Depending on whether or not unit-level data} and sampling are part of the simulation process, the aggregate-level follows the generation of the population or is based on the aggregated sample. %Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.

@@

\red{Seen this way,} \proglang{saeSim} maps the different steps into \proglang{R}. Two layers with separate responsibilities need to be discussed. The first is \textit{how} different simulation components can be combined, and the second is \textit{when} they are applied. Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component. To be precise, we use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value. The return value of one component is the input of the next. This definition of interfaces is used for all existing tools in \proglang{saeSim}. The second column in Figure \ref{fig:flowdiagram} shows how the different steps in a simulation can be accessed. It is important to note that the functions in Figure \ref{fig:flowdiagram} control the process, the second layer, i.e. \textit{when} components are applied. Each of these functions take a simulation setup object to be modified and a function with the discussed interface as arguments. Hence, the pipe operator (\proglang{\%>\%}) can be used to combine separate components to a simulation setup.

\section{Case studies}
\label{sec:caseStudy}
We present two applications of \proglang{saeSim}, one model-based simulation in Section \ref{sec:csModel} and a design-based simulation in Section \ref{sec:csDesign}. \red{First though, we} introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation. The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}. As a simple example see the following lines which are equivalent with respect to their functionality:

@@

Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we notice that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme. \red{\proglang{sim\_sample} is responsible as a control} when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples. Separating the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process. The composition of a simulation in that manner will focus on the definition of components and hide control structures. Any function can be passed to \proglang{sim\_sample} which has a \proglang{data.frame} both as input and as return value. The only responsibility of that function is to draw a sample, which makes it easy to find, understand and reuse when published. The operator \proglang{\%>\%} is used to add new components to the setup.

@@

Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows (the head) of the resulting data table are printed. This enables interactivity with the object \red{itself; however, it hides the fact that the setup} object is a collection of functions to be called. In this model the error component $e_i$ has different variances which is not covered by a predefined function. Thus, as a \textit{generator component}, we define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:

@@

To add the area-level predictions from a Fay-Herriot model we need to define another component. The function takes a \proglang{data.frame} as input and returns the modified version. For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}. \red{Hence we }define a function named \proglang{comp\_FH} and add it to the process:

@@

An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios. \red{Currently we do} not provide further tools to process the resulting data as there are many tools readily available in \proglang{R}. In the design-based scenario we show how to process the result data into graphs with only a few lines of code.

@@

In the design-based simulation we illustrate the use of \proglang{saeSim} under a fixed population. For this purpose we use a synthetic population generated from Austrian EU-SILC (European Union Statistics on Income and Living Conditions) data. The data consists of 25 thousand households. It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is also used as an example data set. To keep this study as simple as possible, \red{we further restrict the data to the main income holder} and only use some of the provided auxiliary information.

@@

Before we come to the estimation, the first step is to add a sampling scheme. As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data. Then the sampling component is added, \red{where the definition is to draw 10 per cent samples} of the observations from each domain with simple random sampling.
